\documentclass[a4paper]{article}

\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{fancyhdr}

\newcommand{\theDate}{June 24th, 2017} %Change this every meeting
\setlength{\headheight}{13.6pt}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot[L]{Capstone Meeting Minutes}
\fancyfoot[R]{\theDate{}}
\fancyfoot[C]{\thepage}

\begin{document}
	\begin{center}
		\huge Capstone Meeting Minutes
	\end{center}
	\textbf{Attendance} Farhan Rahman, Wyatt Thomson, Huy Bui, James Jo, Aleksa Svitlica (Note Taker) \\
	\textbf{Regrets} None \\

	\section{Old business}
	\subsection{Follow up on old ideas}
	\begin{itemize}
		\item Certain ideas like the satellite and vanta black are probably out of consideration.
		\item We have decided to shelf the telepresence robot for the time being and focus on the self driving car network
		\item Self driving car network using zigbee. Each car could be a node in a peer to peer network.
		\item We need to do cost analysis for the hardware of the cars. They each need wheels, a processor and radio module at least.
		\item Security is not built into zigbee, therefore if we decide to use zigbee we will need to implement some basic encryption.
	\end{itemize}

	\section{New business}
	\subsection{Proposal}
	Our sample propsal should be structured roughly like this:
	\begin{itemize}
		\item Title
		\item Abstract
		\item Outline of research (citations) to show it is feasible
		\item Outline of technology and hardware we are being used.
		\item What we would be working on and how we are dividing these tasks.
	\end{itemize}
	\subsection{Roadmap}
	\begin{itemize}
		\item We still need to create a roadmap. Perhaps something like a Gantt chart if we want a strict structure or something less formal.
		\item Farhan has added some rough dates on Slack.
	\end{itemize}


	\section{Actions to be taken}
	\subsection{High Priority}
	\begin{itemize}
 		\item None
	\end{itemize}
	\subsection{Low Priority}
	\begin{itemize}
		\item \textbf{Everyone:} Autonomous guidance research. Path routing. Collision detection.
		\item \textbf{Everyone:} Zigbee research. Implementing neural networks.
	\end{itemize}
	\textbf{Meeting ended at 2:00.}
\end{document}
